Wikipedia Text Mining and Entropy Analysis

### 2019-03-14 wiki_entropy/wiki_clustering.Rmd
mean imputation for testing

@@

wa <- fair_wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(x1a:x19a, language) %>%
  group_by(language) %>%
  slice(1)

@@

wa_sub <- wa %>%
  filter(language %in% wa_langs) %>%
  column_to_rownames("language")
 # mutate_each(~as.numeric(as.factor(.x)))

wa_out <- wa_sub %>%
  select(-x14a:-x17a, -x9a,-x10a) %>%
  slice(1:5) %>%
  MIMCA(ncp = 1)

>>>>

mean_wf <- fair_wf

mean_impute <- function(col) {
  counts <- col %>%
    remove_missing() %>%
    unlist() %>%
    table() %>%
    sort(decreasing = T) 
  col[is.na(col),] <- labels(counts[1])
  return(col)
}

for (i in 1:ncol(mean_wf)) {
  mean_wf[, i] <- mean_impute(mean_wf[, i])
}

@@

wa <- fair_wf %>% 
  select(x1a:x10a, language) %>%
  group_by(language) %>%
  slice(1)

@@

wa_sub <- wa %>%
  filter(language %in% wa_langs) %>%
  column_to_rownames("language") %>%
  ungroup()
 # mutate_each(~as.numeric(as.factor(.x)))

wa_out <- wa_sub %>%
  MIMCA(ncp = 1)
